The \dealii{} Library, Version 8.5

### 2017-03-09 8.5/paper.tex
unify punctuation

\author[5]{Luca Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy
{\texttt{luca.heltai@sissa.it}}}

@@

\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}

>>>>

\author[5]{Luca Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
{\texttt{luca.heltai@sissa.it}}}

@@

\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}
